Let time $t \geq 0, t \in \Q$.
Let $t = n \tau$ where $n \in \Nz$ (Discrete Time).

Let $m \in \N, \lall i\in \N, 1 \leq i \leq m$:
$\bm{S_i(n)}$ is the price of the $i$th \textbf{Risky Asset} at time $n$,
with a total of $m$ risky assets. 

$\bm{A(n)}$ is the price of the \textbf{Risk-Free Asset} at time $n$.

Unless stated otherwise, $A(0)$ is used as a reference, with $A(0) = 1$ or $100$.

A \textbf{Portfolio} is a vector $\vec{v}(n) = \vectorvalue{x_1(n), \hdots , x_m(n), y(n)}$
representing the amount of assets held between time $n - 1$ and time $n$, 
where $\vec{v}(0)$ is undefined.
Let the \textbf{Value} of the Portfolio at time $n$ being
\[
    \bm{V(n)} = 
    \begin{cases}
        y(1)A(0) + \sum_{j=1}^m x_j(1)S_j(0) &\text{for $n = 0$ (Initial Value/Wealth)} \\
        y(n)A(n) + \sum_{j=1}^m x_j(n)S_j(n) &\text{for $n > 0$}
    \end{cases}
\]

\textbf{Rate of Return} TODO**** $K_i = $return of $S_i$ is $\bm{K_F} = \frac{F(1) - F(0)}{F(0)}$.

Six Assumptions: 
\begin{enumerate}
    \item $\lall n > 0, S(0), A(0), A(n)$ are known, while $S(n)$ is a random variable (Randomness).
    \item $\lall n, S(n) > 0 \land A(n) > 0$ (Positivity of Prices).
    \item $\lall i, \lall n, x_i(n) \in \R,y(n) \in \R$ (Divisibility, Liquidity and Short Selling).
    \item $\lall n, V(n) \geq 0$ (Solvency).
    \item $\lall n, S(n)$ can only have a finite number of values (Discrete Unit Prices).
    \item $\lall n > 0, V(0) = 0 \lif V(n) = 0$ (No-Arbitrage Principle).
\end{enumerate}

An Investment Strategy is \textbf{Self-Financing}
$\iff$
\(
    \lall n \geq 1,
    V(n) = y(n + 1)A(n) + \sum_{j=1}^m x_j(n + 1)S_j(n)
\)

An Investment Strategy is \textbf{Predictable}
$\iff$
$\lall n,$ the Portfolio $\vec{v}(n + 1)$
constructed at time $n$ only depends on previous Portfolios.

An Investment Strategy is \textbf{Admissible}
$\iff$
it is Predictable, Self-Financing and Assumption 6 (?).

% % Scrap
% Let there be $m$ risky assets $x_1 S_1(n), \hdots , x_mS_m(n)$.
% Let the risk-free asset $A(0) = 1$.

% Let $t \in \set{0,1}$.

% $\bm{(x,y)}$ is a \textbf{Portfolio},
% where the value of the Portfolio is $\bm{V(t)} = xS(t) + yA(t)$.

% Let $F \in \set{S,A,V}$.
% \textbf{Rate of Return} is $\bm{K_F} = \frac{F(1) - F(0)}{F(0)}$.

TODO (Fundamental Theorem of Asset Pricing, Page 83)
(Extended Model with Derivative securities, very simular)

A \textbf{Forward Contract} is an agreement to exchange a Risky Asset
at a future \textbf{Delivery Date} for a \textbf{Forward Price $\bm{F}$}.\\
To sell is to take a \textbf{Short Forward Position}.
To buy is to take a \textbf{Long Forward Position}.

A \textbf{Call Option} is a contract that gives the holder a right/option 
to purchase a Risky Asset at a furture \textbf{Exercise Time} for a \textbf{Strike/Exercise Price}.
Let $\bm{C(t)}$ denote the price of the option at time $t$.

The prices for Options and Forward Contracts are determined by the No-Arbitrage Principle.

Options are a derivative asset.